Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-10-01 paper.tex
add closing paragraph and neup logo

@@

TODO: thank ross maybe for vision-sourced inspiration about modeling effects
TODO: thank neup and add neup logo

>>>>

The value of realism in fuel cycle modeling is greatly be enhanced by an
associated understanding of how outcomes are affected by added fidelity.
Cyclus' flexibility for accomodating different modeling choices uniquely
enables many interesting comparisons.  Continued work in this direction has
great potential to to improve the integrity of fuel cycle analysis generally.

@@

TODO: thank ross maybe for vision-sourced inspiration about modeling effects

This research is being performed in part using funding received from the DOE
Office of Nuclear Energy's Nuclear Energy University Programs.  The authors
thank the NEUP for its generous support.

\begin{center}
\includegraphics[width=1.5in]{neup_logo_large.jpg}
\end{center}
